---
title: "JLS_Replay_Reset Paper"
author: "Kirk Vanacore"
date: "5/5/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# How reward- and error-based feedback systems create micro-failures to support learning strategies




```{r packages, include=FALSE}
# prepare libraries
library(dplyr)
library(psych)
library(ggplot2)
library(sjPlot)
library(lme4)
library(tidyverse)
library(splitstackshape)
library(reshape2)
library(stringr)
library(nnet)
library(lavaan)
library(OpenMx)
library(semPlot)
library(DBI)
library(naniar)
library(ggthemes)
library(plotROC)
library(pROC)
options(max.print=1000000)
options(scipen = 100)
gc()
```

## Data

```{r load data}
ies_research_con <- dbConnect(RSQLite::SQLite(), "/Users/kirkvanacore/Documents/WPI Analyses/MAPLE_IES_DB_Creation/ies_research schema/maple_ies_research.db")

dat <- dbGetQuery(ies_research_con, 
"Select a.StuID,
        sr.SchIDPre,
        sr.SchIDEnd,
        sd.race_ethnicity,
        sd.IEP,
        sd.ESOL,
        a.pre_total_math_score,
        a.pre_MA_avg_score,
        a.pre_MA_total_score,
        a.post_total_math_score,
        sp.problem_id,
        sp.total_replay,
        IIF( sp.total_replay >= 1, 1, 0)  as any_replay,
        sp.first_num_steps,
        sp.first_clovers,
        sp.first_num_errors,
        sp.first_num_hints,
        sp.first_num_resets,
        sp.first_start_time,
        sp.first_end_time,
        sp.best_num_steps,
        sp.best_clovers,
        sp.best_num_errors,
        sp.best_num_hints,
        sp.best_num_resets,
        sp.best_start_time,
        sp.best_end_time,
        sp.total_completed_attempts,
        pm.optimal_steps,
        pm.optional,
        pm.tutorial
from fh2t_student_problem sp
    inner join assess_student a on a.StuID = sp.StuID
    inner join student_roster sr on sr.StuID = sp.StuID 
    inner join student_demo sd on sd.StuID = sp.StuID
    inner join fh2t_problems_meta pm on pm.problem_id = sp.problem_id
    inner join crosswalk_student cw on cw.StuID = sp.StuID
    and cw.condition_assignment = 'FH2T' 
      where sr.DROPSCH1 = 0 and sr.DROPSCH2 = 0   ;
    
 ")
colnames(dat)

demo_data_all_FH2T <- dbGetQuery(ies_research_con,
                                 "select sd.*  
from student_demo sd
inner join student_roster sr
 on sd.StuID = sr.StuID
where sr.DROPSCH1 = 0 and 
rdm_condition = 'FH2T'"

)

table(dat$first_clovers)
table(dat$first_clovers, dat$first_num_resets)

table(is.na(dat$first_clovers), is.na(dat$first_num_resets))

length(unique(dat$StuID))
length(unique(dat$problem_id))

# no duplicates
length(unique(paste(dat$problem_id, dat$StuID)))

# create next problem clovers
dat <- dat %>%
  arrange(StuID, problem_id) %>%
  group_by(StuID) %>%
  mutate(
    next_problem_first_clovers = lead(first_clovers)
  )

check <- dat %>%
  select(StuID,
         problem_id,
         first_clovers,
         next_problem_first_clovers)

# dat <- dat %>%
#   replace_with_na_all(~.x == "#NULL!")

# analysis data

# make sure only the study schools are included
table(dat$SchIDPre)
table(dat$SchIDEnd)

# pretest algebra score
dat$pre_total_math_score <- ifelse(dat$pre_total_math_score == "#NULL!", NA, dat$pre_total_math_score)
dat$pre_total_math_score <- as.numeric(dat$pre_total_math_score)
# pretest math anxiety 
dat$pre_MA_total_score <- ifelse(dat$pre_MA_total_score == "#NULL!", NA, dat$pre_MA_total_score)
dat$pre_MA_total_score <- as.numeric(dat$pre_MA_total_score)

ad <- dat %>%
  filter(
         SchIDEnd != "#NULL!",
         is.na(pre_MA_total_score) == F,
         is.na(pre_total_math_score) == F
         )

table(ad$SchIDEnd)


table((dat$first_clovers))
table(is.na(dat$first_clovers))

table((ad$first_clovers))
table(is.na(ad$first_clovers))

table(dat$total_completed_attempts)
table(ad$total_completed_attempts)

# student level aggigation
ad <- ad %>%
  group_by(StuID) %>%
  mutate(
    avg_clovers = mean(first_clovers),
    num_problems = length(problem_id)
  ) %>%
  ungroup() %>%
  group_by(problem_id) %>%
  mutate(
    prob_avg_clovers = mean(first_clovers),
    prob_num_problems = length(problem_id)
  ) 

describe(ad$avg_clovers)
hist(ad$avg_clovers)

# errors
ad$first_error_any <- ifelse(ad$first_num_errors > 0, 1,0)

describe(ad$prob_avg_clovers)
hist(ad$prob_avg_clovers)
plot(ad$prob_avg_clovers,
     ad$prob_num_problems)

write_csv(ad, "Anxiety_analysis_data.csv")

```
## Sample

```{r}
### Number of students
length(unique(ad$StuID))

### Number of problems
length(unique(ad$problem_id))

### Number of students
length((ad$problem_id))

# Race ethnicity
# "1 = Hispanic/Latino, 
# 2 = American Indian/Alaska Native, 
# 3 = Asian, 
# 4 = Black/African American, 
# 5 = Native Hawaiian or Other Pacific islander
# 6 = White, 
# 7 = Two or more races "

students <- ad %>%
  ungroup() %>%
  select(
    StuID, 
    race_ethnicity,
    pre_total_math_score,
    pre_MA_total_score
  ) %>%
  mutate(
  race_ethnicity = dplyr::recode(
   as.character(race_ethnicity),
    "1" = "Hispanic/Latino", 
    "2" = "American Indian/Alaska Native",
    "3" ="Asian",
    "4" = "Black/African American",
    "5" = "Native Hawaiian or Other Pacific islander",
    "6" = "White",
    "7" = "Two or more races"
 )
  ) %>%
  distinct()

# missing data for Anayltic sample
table(is.na(students$race_ethnicity))
table(is.na(students$race_ethnicity))/(length(students[]$race_ethnicity))

table(students$race_ethnicity)
round(
table(students[is.na(students$race_ethnicity) == F, ]$race_ethnicity)/length(students[is.na(students$race_ethnicity) == F, ]$race_ethnicity)*100, 2)


### Demo data for total FH2T Sample
table(is.na(demo_data_all_FH2T$race_ethnicity))
table(is.na(demo_data_all_FH2T$race_ethnicity))/(length(demo_data_all_FH2T[]$race_ethnicity))

table(demo_data_all_FH2T$race_ethnicity)
round(
table(demo_data_all_FH2T[is.na(demo_data_all_FH2T$race_ethnicity) == F, ]$race_ethnicity)/length(demo_data_all_FH2T[is.na(demo_data_all_FH2T$race_ethnicity) == F, ]$race_ethnicity)*100, 2)


# test for differences overall (analytic/randomized)
chisq.test(rbind(table(demo_data_all_FH2T$race_ethnicity),
           table(students$race_ethnicity)))
# test for differences b/w each raical group (analytic/randomized)

# white 
chisq.test(cbind(
  rbind(table(demo_data_all_FH2T$race_ethnicity == 6),
           table(students$race_ethnicity== "White"))
  
))

# asian 
chisq.test(cbind(
  rbind(table(demo_data_all_FH2T$race_ethnicity == 3),
           table(students$race_ethnicity== "Asian"))
  
))

# Hispanic 
chisq.test(cbind(
  rbind(table(demo_data_all_FH2T$race_ethnicity == 1),
           table(students$race_ethnicity== "Hispanic/Latino"))
  
))
# Black/African American 
chisq.test(cbind(
  rbind(table(demo_data_all_FH2T$race_ethnicity == 4),
           table(students$race_ethnicity== "Black/African American"))
  
))

# American Indian/Alaska Native 
chisq.test(cbind(
  rbind(table(demo_data_all_FH2T$race_ethnicity == 2),
           table(students$race_ethnicity== "American Indian/Alaska Native"))
))


# Two or more races
chisq.test(cbind(
  rbind(table(demo_data_all_FH2T$race_ethnicity == 7),
           table(students$race_ethnicity== "Two or more races"))
))

# missing
chisq.test(cbind(
  rbind(table(is.na(demo_data_all_FH2T$race_ethnicity)),
           table(is.na(students$race_ethnicity)))
))

## IEP
table(is.na(students$IEP))
table(students$IEP)
table(students$IEP)/ length(students$IEP)

table(is.na(demo_data_all_FH2T$IEP))
table(demo_data_all_FH2T$IEP)
table(demo_data_all_FH2T$IEP)/ length(demo_data_all_FH2T$IEP)


chisq.test(
rbind((table(demo_data_all_FH2T$IEP)),
           (table(students$IEP)))
)

## ESOL
table(is.na(students$ESOL))
table(students$ESOL)
table(students$ESOL)/ length(students$IEP)

table(is.na(demo_data_all_FH2T$ESOL))
table(demo_data_all_FH2T$ESOL)
table(demo_data_all_FH2T$ESOL)/ length(demo_data_all_FH2T$IEP)

chisq.test(
rbind((table(demo_data_all_FH2T$ESOL)),
           (table(students$ESOL)))
)



```

1 = Hispanic/Latino,
2 = American Indian/Alaska Native,
3 = Asian,
4 = Black/African American,
5 = Native Hawaiian or Other Pacific islander
6 = White,
7 = Two or more races "


## Analyses


### Descriptive Statsitics
``` {r Descriptives Assumptions, warning = FALSE}
# table for continuous variables
kableExtra::kable(
  table<-round(describe(students %>%
                          ungroup() %>%
             select(pre_total_math_score,
                    pre_MA_total_score) ), 2),
  
)

range(scale(students$pre_total_math_score))
table(scale(students$pre_total_math_score) >= 2)

ggplot(students, aes(x= pre_total_math_score)) +
  geom_histogram(bins = 10 )+
  labs(
    title = "Algebraic Knowledge Assessment"
  ) +
  theme_economist()

range(scale(students$pre_MA_total_score))
table(scale(students$pre_MA_total_score) <= 2)

ggplot(students, aes(x= pre_MA_total_score)) +
  geom_histogram(bins = 15 )+
  labs(
    title = "Math Anxiety Assessment"
  ) +
  theme_economist()
```

## RQ1)
(a) We will conduct a multi-level logistic regression using pretest math score, pretest math anxiety score, gender, race/ethnicity, and whether students made an error to predict whether students reset a problem or not. 
	Model 1.1: reset (yes/no) ~ pretest math score + pretest math anxiety score + gender + race/ethnicity + error made + (1|student) + (1|problem)
	(b) We will conduct a multi-level logistic regression using pretest math score, pretest math anxiety score, gender, race/ethnicity, whether students made an error, and the number of clovers earned to predict whether students replayed a problem or not. 
		Model 1.2: replay (yes/no) ~ pretest math score + pretest math anxiety score + gender + race/ethnicity + error made + 2 clovers earned + 3 clovers earned + (1|student) + (1|problem)

```{r}

#Model 1.2: replay (yes/no) ~ pretest math score + pretest math anxiety score + gender + #race/ethnicity + error made + 2 clovers earned + 3 clovers earned + (1|student) + (1|problem)



# confirm no NAs
table(is.na(ad$any_replay))
table(is.na(ad$first_clovers))
table(is.na(ad$first_error_any))
table(is.na(ad$first_num_errors))

# replay
table(ad$any_replay)
round((table(ad$any_replay)/length(ad$any_replay))*100, 2)

# first clovers - dummy code
length(ad$first_clovers)
table(ad$first_clovers)
round((table(ad$first_clovers)/length(ad$first_clovers))*100, 2)

  # dummy code clovers
table(is.na(ad$first_clovers))
  ad$first_clovers_dummy_1 <- ifelse(ad$first_clovers == 1, 1, 0 )
  table(ad$first_clovers_dummy_1, ad$first_clovers)
  ad$first_clovers_dummy_2 <- ifelse(ad$first_clovers == 2, 1, 0 )
    table(ad$first_clovers_dummy_2, ad$first_clovers)
  ad$first_clovers_dummy_3 <- ifelse(ad$first_clovers == 3, 1, 0 )
    table(ad$first_clovers_dummy_3, ad$first_clovers)

  
  # clovers by replay
  table(ad$first_clovers, ad$any_replay)
    # % replay clovers =1
    round((table(ad[ad$first_clovers == 1, ]$any_replay)/
             length(ad[ad$first_clovers == 1, ]$any_replay))*100, 2)
    # % replay clovers =2
    round((table(ad[ad$first_clovers == 2, ]$any_replay)/
             length(ad[ad$first_clovers == 2, ]$any_replay))*100, 2)
    # % replay clovers =3
    round((table(ad[ad$first_clovers == 3, ]$any_replay)/
             length(ad[ad$first_clovers == 3, ]$any_replay))*100, 2)
    
# errors
ad$first_error_any <- ifelse(ad$first_num_errors > 0, 1,0)

table(ad$first_error_any)
round((table(ad$first_error_any)/length(ad$first_error_any))*100, 2)
    
    table(ad$first_error_any, ad$any_replay)
    # % replay errors = 1
    round((table(ad[ad$first_error_any == 1, ]$any_replay)/
             length(ad[ad$first_error_any == 1, ]$any_replay))*100, 2)
    # % replay errors = 0
    round((table(ad[ad$first_error_any == 0, ]$any_replay)/
             length(ad[ad$first_error_any == 0, ]$any_replay))*100, 2)
    



ggplot(ad, aes(x= first_num_errors)) +
  geom_histogram(bins = 100 ) +
  theme_economist()


# change in efficiency
ad$step_change <- ad$best_num_steps - ad$first_num_steps
table(ad$step_change)
table(ad$any_replay, ad$step_change)
ggplot(ad, aes(x= step_change)) +
  geom_histogram(bins = 100 ) +
  theme_economist()
ggplot(ad[ad$step_change != 0, ], aes(x= step_change)) +
  geom_histogram(bins = 100 ) +
  theme_economist()

table(ad[ad$any_replay == 1, ]$step_change !=0 )

ad$step_change_any <- ifelse(ad$step_change != 0, 1, 0)


table(ad[ad$any_replay == 1 & ad$first_clovers != 3, ]$step_change_any)
round((table(ad[ad$any_replay == 1 & ad$first_clovers != 3, ]$step_change_any)/
  length(ad[ad$any_replay == 1 & ad$first_clovers != 3, ]$step_change_any) )*100, 2)


# reach optimal clovers (ie get 3 stars)
ad$reach_optimal_steps <- ifelse(is.na(ad$best_clovers), NA,
            ifelse(ad$best_clovers == 3, 1, 0))

table(ad$best_clovers, ad$reach_optimal_steps)

table(ad$first_clovers, ad$reach_optimal_steps)

table(ad[ad$any_replay == 1 & ad$first_clovers != 3, ]$reach_optimal_steps)


table(ad[ad$any_replay == 1 & ad$first_clovers != 3, ]$reach_optimal_steps)
round((table(ad[ad$any_replay == 1 & ad$first_clovers != 3, ]$reach_optimal_steps)/
  length(ad[ad$any_replay == 1 & ad$first_clovers != 3, ]$reach_optimal_steps) )*100, 2)





```

#### Models
(a) We will conduct a multi-level logistic regression using pretest math score, pretest math anxiety score, gender, race/ethnicity, and whether students made an error to predict whether students reset a problem or not. 
	Model 1.1: reset (yes/no) ~ 
	  pretest math score + 
	  pretest math anxiety score + 
	  gender + race/ethnicity + 
	  error made + (1|student) + (1|problem)
``` {r RQ 1}
hist(ad$first_num_resets)
table(ad$first_num_resets == 0)/length(ad$first_num_resets) 

RQ1_1 <- glmer(
  first_num_resets > 0 ~
    first_error_any +
    scale(pre_MA_total_score) +
    scale(pre_total_math_score) +
    (1|StuID) +
    (1|problem_id),
  family = binomial(),
  data = ad 
  )
summary(RQ1_1)
```	

	
	(b) We will conduct a multi-level logistic regression using pretest math score, pretest math anxiety score, gender, race/ethnicity, whether students made an error, and the number of clovers earned to predict whether students replayed a problem or not. 
		Model 1.2: replay (yes/no) ~ pretest math score + pretest math anxiety score + gender + race/ethnicity + error made + 2 clovers earned + 3 clovers earned + (1|student) + (1|problem)
``` {r RQ 1}
RQ1_2 <- glmer(
  any_replay ~
    first_clovers_dummy_2 +
    first_clovers_dummy_3 +
    first_error_any +
    scale(pre_MA_total_score) +
    scale(pre_total_math_score) +
    (1|StuID) +
    (1|problem_id),
  family = binomial(),
  data = ad 
  )
summary(RQ1_2)

```

##RQ2) 
	(a) We will build on the model used for RQ1a and add an interaction between pretest math anxiety and whether students made an error.
		Model 2.1: reset (yes/no) ~ pre MA + pre math score + gender + race/ethnicity + error made on first problem attempt + (error * pre MA) + (1|student) + (1|problem)
``` {r RQ 1}
hist(ad$first_num_resets)
table(ad$first_num_resets == 0)/length(ad$first_num_resets) 
ad$pre_MA_total_score_high <- (ad$pre_MA_total_score-27)
RQ2_1 <- glmer(
  first_num_resets > 0 ~
    first_error_any*(pre_MA_total_score_high)  +
    scale(pre_total_math_score) +
    (1|StuID) +
    (1|problem_id),
  family = binomial(),
  data = ad 
  )
summary(RQ2_1)
```	

		
		
	(b) We will build on the model used for RQ1b and add an interaction between pretest math anxiety and 2 clovers earned, as well as pretest math anxiety and 3 clovers earned.
		Model 2.2: replay (yes/no) ~ pre MA + pre math score + gender + race/ethnicity + error on first problem attempt + 2 clovers earned after first problem attempt + 3 clovers earned after first problem attempt + (2 clovers * pre MA) + (3 clovers * pre MA) + (1|student) + (1|problem)
		
``` {r RQ 1}
RQ2_2 <- glmer(
  any_replay ~
    first_clovers_dummy_2 +
    first_clovers_dummy_3 +
    first_error_any*
    scale(pre_MA_total_score) +
    scale(pre_total_math_score) +
    (1|StuID) +
    (1|problem_id),
  family = binomial(),
  data = ad 
  )
summary(RQ2_2)

```