---
title: "FH2T Replay_ISLS"
date: "11/12/2021"
output: html_document
---

Preparing libraries & merging datasets. 

Primarily using the aggregate csvs for FH2T, merged with info from demographics, assessments, etc.

For the conference paper, we're mostly using overall level data, as well as demographics & assessment data. May need problem-level data for the clovers plot.

# Packages 
```{r setup, include=FALSE}

# prepare libraries
library(dplyr)
library(psych)
library(ggplot2)
library(sjPlot)
library(lme4)
library(tidyverse)
library(splitstackshape)
library(reshape2)
library(stringr)
library(nnet)
options(max.print=1000000)
gc()
```


# Data Prep 
## Load/Merge/Structure
```{r}
#### imported cleaned & merged data files ####
# the FH2T data from overall- to problem-level
data_all_levels <- read.csv("data/2021-03-25-wpi_ies_study_fall_20_aggregation_table.csv",
                            na.strings = c("N/A")) 

# the existing merged overall & demographics dataset
data_overall_level_demo <- read.csv("data/FH2T_aggregation_overall_merge_2021_03_25.csv",
                            na.strings = c("N/A")) 

# the pre/post test data
data_assessments <- read.csv("data/Assessment_merged_2021_07_16_state_assessment.csv",
                            na.strings = c("N/A")) 
colnames(data_assessments)

#### create WIDE merged file ####

# select variables form all levels data 
for_merging_all_levels <- data_all_levels %>%
  dplyr::select(
    studentID,
    starts_with("o"),
    starts_with("p") &
      ends_with("_goback"),
    starts_with("p") &
      ends_with("_completed") &
      !contains("first"),
    starts_with("p") &
      ends_with("_clover_first"),
    starts_with("p") &
      ends_with("_clover_last"),
    starts_with("p") &
      ends_with("_error"),
    starts_with("p") &
      ends_with("_reset"),
  ) 
colnames(for_merging_all_levels)
# merge with student level data
WIDE_merged_all_levels <- for_merging_all_levels %>%
    inner_join(
      data_overall_level_demo %>%
        select(
          student_number,
          student_id,
          xref,
          final_school_id,
          final_teacher_class,
          final_teacher_id,
          GIFTED,
          ESOL,
          ESOL_FORMER,
          IEP,
          MALE,
          FEMALE,
          student_raceEthnicityFed,
          student_hispanicEthnicity,
          PerformanceLevel
        ) %>%
        rename(studentID = xref),
      by = "studentID"
    ) %>% # n = 1184
    inner_join(
      data_assessments %>%
        select(
          student_id,
          ScaleScore_5th.grade,
          PerformanceLevel_5th.grade,
          Scale.Score_7th.grade,
          Performance.Level_7th.grade,
          math_score_7th.grade,
          pre.total_math_score,
          mid.total_math_score,
          post.total_math_score,
          pre_MA_avg_score,
          pre_MA_total_score,
          post_MA_avg_score,
          post_MA_total_score,
          delayed.total_math_score
        ) # selecting used variables from data_assessments
      ,
      by = "student_id"
    ) # n = 1184
  


#### create LONG merged file ####
View(as.data.frame(colnames(for_merging_all_levels)))

for_merging_all_levels_LONGFULL <-for_merging_all_levels %>%
#  select(names(for_merging_all_levels[1:1000])) %>%
  select(-starts_with("o_")          ) %>%
  melt(id = "studentID", variable.factor=FALSE) 
colnames(for_merging_all_levels_LONGFULL)
table(for_merging_all_levels_LONGFULL$variable)
for_merging_all_levels_LONGFULL$variable1 <-
  str_split(string = for_merging_all_levels_LONGFULL$variable, 
           pattern = '_', 
           n = 2,
           simplify = F) 

for_merging_all_levels_LONGFULL <- for_merging_all_levels_LONGFULL %>% 
      unnest(variable1) %>% 
      group_by(studentID, variable) %>% 
      mutate(problem = seq_along(variable1)) %>% # add a column indicator
      spread(key= problem, value = variable1)

for_merging_all_levels_LONGFULL <- for_merging_all_levels_LONGFULL %>%
  ungroup() %>%
      select(-variable)


colnames(for_merging_all_levels_LONGFULL)
colnames(for_merging_all_levels_LONGFULL) <- c("studentID",
                                               "value",
                                               "problem",
                                               "name")


for_merging_all_levels_LONGFULL  <- for_merging_all_levels_LONGFULL %>%
  group_by(studentID, 
           problem) %>%
  pivot_wider(names_from = name, 
              values_from = value)
colnames(for_merging_all_levels_LONGFULL)
table(for_merging_all_levels_LONGFULL$problem)


# add in student level data
LONG_merged_all_levels <- for_merging_all_levels_LONGFULL %>%
  left_join(
    data_all_levels %>%
      dplyr::select(
        studentID,
        o_distinct_completed,
        o_percent_gobacks,
        o_percentage_reset, 
        o_percent_error
      ),
    by = "studentID"
  ) %>%
  inner_join(
    data_overall_level_demo %>%
      select(
        student_number,
        student_id,
        xref,
        final_school_id,
        final_teacher_class,
        final_teacher_id,
        GIFTED,
        ESOL,
        ESOL_FORMER,
        IEP,
        MALE,
        FEMALE,
        student_raceEthnicityFed,
        student_hispanicEthnicity,
        PerformanceLevel
      ) %>%
      rename(studentID = xref),
    by = "studentID"
  ) %>% # n = 1184
  inner_join(
    data_assessments %>%
      select(
        student_id,
        ScaleScore_5th.grade,
        PerformanceLevel_5th.grade,
        Scale.Score_7th.grade,
        Performance.Level_7th.grade,
        math_score_7th.grade,
        pre.total_math_score,
        mid.total_math_score,
        post.total_math_score,
        pre_MA_avg_score,
        pre_MA_total_score,
        post_MA_avg_score,
        post_MA_total_score, 
        delayed.total_math_score
      ) # selecting used variables from data_assessments
    ,
    by = "student_id"
  ) # n = 1184


# Save MERGED files

  write.csv(LONG_merged_all_levels, "LONG_merged_all_levels.csv")
  write.csv(WIDE_merged_all_levels, "WIDE_merged_all_levels.csv")

#Clean working environment

# simplify df names
LONG <- LONG_merged_all_levels
WIDE <- WIDE_merged_all_levels

# remove all other data frames
rm(list=setdiff(ls(), c("LONG", "WIDE"))) # X will remain

#LONG <- read.csv("LONG_merged_all_levels.csv")
```

 
# Analytic Sample
```{r}
# Exclude schools that drop the program (S03 & S07) 
table(WIDE$final_school_id)
WIDE_AD <- WIDE %>%
  filter(final_school_id != "S03",
         final_school_id != "S07")

#create anaylsis data
LONG_AD <- LONG %>%
  filter(final_school_id != "S03",
         final_school_id != "S07")

# total original sample
length(unique(LONG_AD$studentID)) #1162 students
length(unique(LONG_AD$problem)) # 252 problems
table(LONG_AD$completed) # 109564

# no missing clover data for students who completed assignments
table(is.na(LONG_AD$clover_first))

# no missing error data for students who completed assignments
table(is.na(LONG_AD$error))

#74 missing pretest scores
table(is.na(WIDE_AD$pre.total_math_score)) 

#134 students missing Math Anxiety scores
table(is.na(WIDE_AD$pre_MA_avg_score)) 

#74 missing pretest scores
table(is.na(WIDE_AD$pre.total_math_score), 
      is.na(WIDE_AD$pre_MA_avg_score)) 
  # all the student who were missing Pretest scores were also missing MA scores

LONG_AD <- LONG_AD %>%
  ungroup() %>%
  filter(is.na(LONG_AD$pre.total_math_score) == F &
         is.na(LONG_AD$pre_MA_avg_score) == F &
         LONG_AD$completed == 1 &
         LONG_AD$clover_first != 0)

# total final sample
length(unique(LONG_AD$studentID)) #1031 students
length(unique(LONG_AD$problem)) # 252 problems
table(LONG_AD$completed) # 74359

# Exclude students who are not in the LONG_AD in the WIDE_AD
WIDE_AD <- WIDE_AD %>%
  inner_join(LONG_AD %>%
               select(studentID) %>%
               distinct(),
             by = "studentID")
#### DEMOGRAPHICS ####
round((table(WIDE_AD$student_raceEthnicityFed)/length(WIDE_AD$student_raceEthnicityFed)*100), 3)

# 1 = Hispanic/Latino, 
# 2 = American Indian/Alaska Native, 
# 3 = Asian, 
# 4 = Black/African American, 
# 5 = Native Hawaiian or Other Pacific islander
# 6 = White, 
# 7 = Two or more races

round((table(WIDE_AD$IEP)/length(WIDE_AD$IEP)*100), 3)
round((table(WIDE_AD$ESOL)/length(WIDE_AD$ESOL)*100), 3)

```

# Frequencies, Descrpitives and Assumptions 

## Student Level Data
```{r}
#### REPLAYS ####

# how many students replay? (i.e. "go back")
# 81% of students (967) go back at least once 
table(WIDE_AD$o_percent_gobacks == 0)/length(WIDE_AD$o_percent_gobacks)

# very positively skewed
describe(WIDE_AD$o_percent_gobacks)
ggplot(data =WIDE,
       aes(o_percent_gobacks)) +
  geom_histogram()

### Problems Complete ####
mean(WIDE$o_distinct_completed)
sum(WIDE$o_tried)

#### RESET ####

# almost all students (98.6%) reset at least once
table(WIDE_AD$o_percentage_reset == 0)/length(WIDE_AD$o_percentage_reset)

#  normal distribution
describe(WIDE_AD$o_percentage_reset)
ggplot(data =WIDE,
       aes(o_percentage_reset)) +
  geom_histogram()


#### REPLAY BY RESET ####
ggplot(data =WIDE,
       aes(o_percent_gobacks, o_percentage_reset )) +
  geom_point()

cor.test(
    WIDE_AD$o_percent_gobacks,
    WIDE_AD$o_percentage_reset)


table(LONG_AD$reset, LONG_AD$goback)/length(LONG_AD$goback)


#### ERRORS ####
# normal
describe(WIDE_AD$o_percent_error)
  ggplot(data =WIDE,
       aes(o_percent_error )) +
  geom_histogram()

  
#### COMPLETIONS ####
#  bimodal distribution (skew and kurtosis are okay )
describe(WIDE_AD$o_distinct_completed)
  ggplot(data =WIDE,
       aes(o_distinct_completed )) +
  geom_histogram()

  
#### DEMOGRAPHICS ####

# race ethnicity
table(WIDE_AD$student_raceEthnicityFed) 
  table(is.na(WIDE_AD$student_raceEthnicityFed) ) #14 missing Demo data

# 1 = Hispanic/Latino, 
# 2 = American Indian/Alaska Native, 
# 3 = Asian, 
# 4 = Black/African American, 
# 5 = Native Hawaiian or Other Pacific islander
# 6 = White, 
# 7 = Two or more races

# dummy code race/ethnicity (white is reference bc it is largest group)
WIDE_AD$Latinx <- ifelse(is.na(WIDE_AD$student_raceEthnicityFed), NA,
                      ifelse(WIDE_AD$student_raceEthnicityFed == 1, 1, 0))
WIDE_AD$Native <- ifelse(is.na(WIDE_AD$student_raceEthnicityFed), NA,
                      ifelse(WIDE_AD$student_raceEthnicityFed == 2, 1, 0))
WIDE_AD$Asian <- ifelse(is.na(WIDE_AD$student_raceEthnicityFed), NA,
                      ifelse(WIDE_AD$student_raceEthnicityFed == 3, 1, 0))
WIDE_AD$Black <- ifelse(is.na(WIDE_AD$student_raceEthnicityFed), NA,
                      ifelse(WIDE_AD$student_raceEthnicityFed == 4, 1, 0))
WIDE_AD$TwoPlusRaces <- ifelse(is.na(WIDE_AD$student_raceEthnicityFed), NA,
                      ifelse(WIDE_AD$student_raceEthnicityFed == 4, 1, 0))

  table(WIDE_AD$student_hispanicEthnicity, WIDE_AD$Latinx) # complete overlap
  
# ESOL  
table(is.na(WIDE_AD$ESOL) ) # 161 MISSING!
table(WIDE_AD$ESOL) 
table(WIDE_AD$ESOL) /length(WIDE_AD$ESOL) # 8.87% (of the students we have data for)

table(WIDE_AD$ESOL_FORMER) # can decide whether we should put these students 

table(is.na(WIDE_AD$MALE))# 161 MISSING!
table(WIDE_AD$MALE, WIDE_AD$FEMALE) # no overlap

# Performance level  --> WHICH YEARS PL DO WE WANT TO USE (Are these the 6th grade levels)
table(WIDE_AD$PerformanceLevel)
WIDE_AD$PerformanceLevel <- ifelse(WIDE_AD$PerformanceLevel == "", NA, WIDE_AD$PerformanceLevel)
table(is.na(WIDE_AD$PerformanceLevel)) # 175 MISSING!

# dummy code permanence levels (Proficient Leaner as reference)
WIDE_AD$Beginning <- ifelse(
  is.na(WIDE_AD$PerformanceLevel),
  NA,
  ifelse(WIDE_AD$PerformanceLevel == "Beginning Learner", 1, 0))

WIDE_AD$Developing <- ifelse(
  is.na(WIDE_AD$PerformanceLevel),
  NA,
  ifelse(WIDE_AD$PerformanceLevel == "Developing Learner", 1, 0))

WIDE_AD$Distinguished <- ifelse(
  is.na(WIDE_AD$PerformanceLevel),
  NA,
  ifelse(WIDE_AD$PerformanceLevel == "Distinguished Learner", 1, 0))

table(WIDE_AD$PerformanceLevel, WIDE_AD$Distinguished)


  table(WIDE_AD$GIFTED, WIDE_AD$PerformanceLevel) # a lot of overlap between gifted and performance levels

#### PERFORMANCE SCORES ####

# researcher created measures
table(is.na(WIDE_AD$pre.total_math_score))
table(is.na(WIDE_AD$post.total_math_score))
  table(is.na(WIDE_AD$pre.total_math_score), is.na(WIDE_AD$post.total_math_score)) # 777 with both scores


describe(WIDE_AD$pre.total_math_score)
ggplot(data =WIDE,
       aes(pre.total_math_score)) +
  geom_histogram()

describe(WIDE_AD$post.total_math_score)
ggplot(data =WIDE,
       aes(post.total_math_score)) +
  geom_histogram()

ggplot(data =WIDE,
       aes(post.total_math_score, pre.total_math_score )) +
  geom_density2d()

cor.test(WIDE_AD$post.total_math_score, WIDE_AD$pre.total_math_score)

# standardized measures
describe(WIDE_AD$ScaleScore_5th.grade)
ggplot(data =WIDE,
       aes(ScaleScore_5th.grade)) +
  geom_histogram()

describe(WIDE_AD$Scale.Score_7th.grade)
ggplot(data =WIDE,
       aes(Scale.Score_7th.grade)) +
  geom_histogram()

cor.test(WIDE_AD$ScaleScore_5th.grade, WIDE_AD$Scale.Score_7th.grade)
cor.test(WIDE_AD$ScaleScore_5th.grade, WIDE_AD$pre.total_math_score)
cor.test(WIDE_AD$Scale.Score_7th.grade, WIDE_AD$post.total_math_score)


#### MATH ANXIETY ####
describe(WIDE_AD$pre_MA_avg_score)
ggplot(data =WIDE,
       aes(pre_MA_avg_score)) +
  geom_histogram(bins = 40)

describe(WIDE_AD$post_MA_avg_score)
ggplot(data =WIDE,
       aes(post_MA_avg_score)) +
  geom_histogram(bins = 40)

```

## Problem Attempt Level Data
```{r}
# dummy code race/ethnicity (white is reference bc it is largest group)
LONG_AD$Latinx <- ifelse(is.na(LONG_AD$student_raceEthnicityFed), NA,
                      ifelse(LONG_AD$student_raceEthnicityFed == 1, 1, 0))
LONG_AD$Native <- ifelse(is.na(LONG_AD$student_raceEthnicityFed), NA,
                      ifelse(LONG_AD$student_raceEthnicityFed == 2, 1, 0))
LONG_AD$Asian <- ifelse(is.na(LONG_AD$student_raceEthnicityFed), NA,
                      ifelse(LONG_AD$student_raceEthnicityFed == 3, 1, 0))
LONG_AD$Black <- ifelse(is.na(LONG_AD$student_raceEthnicityFed), NA,
                      ifelse(LONG_AD$student_raceEthnicityFed == 4, 1, 0))
LONG_AD$TwoPlusRaces <- ifelse(is.na(LONG_AD$student_raceEthnicityFed), NA,
                      ifelse(LONG_AD$student_raceEthnicityFed == 4, 1, 0))


# dummy code permanence levels (Proficient Leaner as reference)
LONG_AD$Beginning <- ifelse(
  is.na(LONG_AD$PerformanceLevel),
  NA,
  ifelse(LONG_AD$PerformanceLevel == "Beginning Learner", 1, 0))

LONG_AD$Developing <- ifelse(
  is.na(LONG_AD$PerformanceLevel),
  NA,
  ifelse(LONG_AD$PerformanceLevel == "Developing Learner", 1, 0))

LONG_AD$Distinguished <- ifelse(
  is.na(LONG_AD$PerformanceLevel),
  NA,
  ifelse(LONG_AD$PerformanceLevel == "Distinguished Learner", 1, 0))

table(LONG_AD$PerformanceLevel, LONG_AD$Distinguished)

table(LONG_AD$clover_first, LONG_AD$goback)


table(LONG_AD$clover_first)
table(LONG_AD$clover_last)
table(is.na(LONG_AD$clover_last)) # no missing --> so if colver first = colver last then 
LONG_AD$clover_change <- LONG_AD$clover_last-LONG_AD$clover_first
table(LONG_AD$clover_change)
table(LONG_AD$reset)


## Clovers
 # dummy code first clovers (0, is reference cat)
table(LONG_AD$clover_first)
LONG_AD$clover_first1 <- ifelse(LONG_AD$clover_first == 1, 1, 0)
LONG_AD$clover_first2 <- ifelse(LONG_AD$clover_first == 2, 1, 0)
LONG_AD$clover_first3 <- ifelse(LONG_AD$clover_first == 3, 1, 0)

table(LONG_AD$clover_change, LONG_AD$goback, LONG_AD$reset)
# this is confusing to me: there seem to be students who had a change in there clovers from first to last, but didn't reset or replay  --> how is this possible
table(LONG_AD$clover_change, LONG_AD$goback == 0 & LONG_AD$reset ==0)

table(LONG_AD$first_error)

table(LONG_AD$error)

### Replay VS Reset
table(LONG_AD$reset) / length(LONG_AD$reset)
table(LONG_AD$goback)/ length(LONG_AD$goback)

# Create Replay/Reset Variable

LONG_AD$replay_reset <- as.factor(ifelse(LONG_AD$goback == 0 & 
                                 LONG_AD$reset == 0, "None",
                               ifelse(LONG_AD$goback == 1 & 
                                 LONG_AD$reset == 1, "Both",
                               ifelse(LONG_AD$goback == 1, "Replay",
                                      ifelse(LONG_AD$reset == 1, "Reset", "NA"
                                             )))))
table(LONG_AD$replay_reset)/length(LONG_AD$replay_reset)
table(LONG_AD$goback, LONG_AD$reset)/ length(LONG_AD$goback)


LONG_AD$replay_reset <- relevel(LONG_AD$replay_reset, ref = "None")


## LOOK INTO TIME AND GO BACKS Is there a difference between time 


### MC math anxiety 
LONG_AD$pre_MA_avg_score_MC <- LONG_AD$pre_MA_avg_score - mean(LONG_AD$pre_MA_avg_score)
describe(LONG_AD$pre_MA_avg_score)
table(is.na(LONG_AD$pre_MA_avg_score))
describe(LONG_AD$pre_MA_avg_score_MC)

```

# RQ1: Which feedback features (Clovers VS Errors) of FH2T precit replay vs reset behavior
  
 "As some powerful statisticians have argued (Begg and Gray, 1984; Allison, 1984, p. 46-47), separate logit models are much more flexible as they permit for the independent specification of the model equation for each contrast.
 ...
 Yes, with some disclaimers. This method is called the “Begg and Gray Approximation”. Begg and Gray (1984, p. 16) showed that this “individualized method is highly efficient”. However, there is some efficiency loss and the Begg and Gray Approximation produces larger standard errors (Agresti 2002, p. 274). As such, it is more difficult to obtain significant results with this method and the results can be considered conservative. This efficiency loss is smallest when the reference category is large (Begg and Gray, 1984; Agresti 2002).
 Agresti, A. (2002). Categorical data analysis (2nd ed.). Hoboken, NJ: John Wiley & Sons.


Begg, C. B., & Gray, R. (1984). Calculation of polychotomous logistic regression parameters using individualized regressions. Biometrika, 71(1), 11-18.
 "
 --> https://stackoverflow.com/questions/21082396/multinomial-logistic-multilevel-models-in-r
```{r}
### MODELS ####
test <- multinom(replay_reset ~ ses + write, data = LONG_AD)

Model_Replay_1 <-  glmer(
  goback ~
    clover_first2 +
    clover_first3 +
    error + # what is the  relation between errors and clovers
    scale(pre.total_math_score) +
    Latinx +
    Native +
    Black +
    TwoPlusRaces +
    ESOL +
    pre_MA_avg_score +
    (1 | problem) +
    (1 | studentID),
  data = LONG_AD,
  family = binomial()
)
summary(Model_Replay_1)

Model_Replay_2 <-  glmer(
  goback ~
    clover_first2 +
    clover_first3 +
    error + # what is the  relation between errors and clovers
    scale(pre.total_math_score) +
    scale(pre_MA_avg_score) +
    (1 | problem) +
    (1 | studentID),
  data = LONG_AD,
  family = binomial()
)
summary(Model_Replay_2)


Model_Reset_1 <-  glmer(
  reset ~
    clover_first2 +
    clover_first3 +
    error + # what is the  relation between errors and clovers
    scale(pre.total_math_score) +
    Latinx +
    Native +
    Black +
    TwoPlusRaces +
    ESOL +
    pre_MA_avg_score +
    (1 | problem) +
    (1 | studentID),
  data = LONG_AD,
  family = binomial()
)
summary(Model_Reset_1)

Model_Reset_2 <-  glmer(
  reset ~
    clover_first2 +
    clover_first3 +
    error + # what is the  relation between errors and clovers
    scale(pre.total_math_score) +
    scale(pre_MA_avg_score) +
    (1 | problem) +
    (1 | studentID),
  data = LONG_AD,
  family = binomial()
)
summary(Model_Reset_2)


Model_Reset_2_cof<-as.data.frame(summary(Model_Reset_2)$coefficients)
colnames(Model_Reset_2_cof)

Model_Replay_2_cof<-as.data.frame(summary(Model_Replay_2)$coefficients)
colnames(Model_Replay_2_cof)

round(p.adjust(Model_Reset_2_cof$`Pr(>|z|)`, method = "BH"), 6)
round(p.adjust(Model_Replay_2_cof$`Pr(>|z|)`, method = "BH"), 6)
round(p.adjust(rbind(Model_Replay_2_cof$`Pr(>|z|)`,
                     Model_Reset_2_cof$`Pr(>|z|)`), method = "BH"), 6)
cbind(Model_Replay_2_cof$`Pr(>|z|)`,
                     Model_Reset_2_cof$`Pr(>|z|)`)


tab_model(
  Model_Replay_2,
  Model_Reset_2
)

tab_model(RQ1_FINAL,
          
  show.aic = T,
  show.r2 = F)

summary(RQ1_FINAL)

```


